Natural Language Interfaces to Structured Data

### 2012-09-17 tr-nlisurvey/src/nli-survey.tex
commit

The way translation from NL questions to formal query has evolved over years.
Table~\ref{tab:overview} presents an overview of major systems that we consider
in the survey.

\begin{table}
\centering
\rotatebox{90}{
\begin{minipage}{\textheight}
\begin{tabular}{|c|l|c|c|c|c|c|c|}\hline
%\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
\multirow{2}{*}{\bf Approach} & \multirow{2}{*}{\bf System}
&
\multicolumn{6}{c|}{\bf Dimensions}\\\cline{3-8}
& & {\bf Query} & {\bf Data} & {\bf Answers} & {\bf Portability} & {\bf
Linguistic coverage} & {\bf Error feedback}\\\hline\hline 
\multirow{2}{*}{Domain-dependent semantic parsing} & {\sc
Baseball}~\cite{Green:1961:BAQ:1460690.1460714} & & & & & & \\\cline{2-8}
& {\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695} & & & & & & \\\hline
\multirow{5}{*}{Complex question translation} & {\sc
Chat-80}~\cite{Warren:1982:EEA:972942.972944} & & & & & & \\\cline{2-8}
& {\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & & & & & & \\\cline{2-8}
& {\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & & & & & & \\\cline{2-8}
& {\sc
Precise}~\cite{Popescu:2004:MNL:1220355.1220376,Popescu:2003:TTN:604045.604070}
& & & & & & \\\cline{2-8}
& {\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & & & & & & \\\hline
\multirow{5}{*}{Feedback-driven approaches} &
{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & & & & & & \\\cline{2-8}
& {\sc Team}~\cite{Grosz:1987:TED:25672.25674} & & & & & & \\\cline{2-8}
& {\sc NaLIX} \& {\sc DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281} & & & & & &
\\\cline{2-8}
& {\sc C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190} & & & & & &
\\\cline{2-8}
& {\sc
Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & & & & & & \\\hline
\multirow{3}{*}{Learning-based approaches} & Zettlemoyer
et al.~\cite{DBLP:conf/uai/ZettlemoyerC05} & & & & & & \\\cline{2-8}
& Miller et al.~\cite{Miller:1996:FSA:981863.981871} & & & & & & \\\cline{2-8}
& {\sc Wolfie}~\cite{Thompson:2003:AWM:1622420.1622421} & & & & & &
\\\hline
\multirow{2}{*}{Schema-unaware approaches} & {\sc
PowerAqua}~\cite{DBLP:conf/esws/LopezMU06} & & & & & & \\\cline{2-8}
 & {\sc DeepQA}~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} & & & & & &
 \\\hline
\end{tabular}
\end{minipage}
}
\caption{Overview of major NL interfaces to structured data}
\label{tab:overview}
\end{table}

@@

\subsection{Schema-unaware approaches}
A range of recent systems aggregate potential answers from different sources.
This range of systems have emerged in parallel with the success of the semantic
web technologies. 
The particularity of these approaches, is that they cannot rely on the schema of
underlying knowledge bases, because the different sources are potentially
modelled in very different ways. 
Thus, the set of systems represented by these approaches try to bridge the gap
between user terminologies and the different terminologies used in the different
knowledge bases that the interface talks to.
These approaches can be seen as an extension of several approaches presented
before, namely ``complex question translation'' (because the question is
further analyzed to map it with the terminology used in the different knowledge
bases) and ``learning-based approaches'' (because some of the systems
represented in these approaches comprise learning components).

\subsubsection{Terminology mapping}
In previous approaches, end-users were not aware of how data are modeled in the
knowledge base. This requires advanced natural language processing to map user's
terminology with database terminology. In schema-unaware apppraoches, the
systems do not talk to a single database, but to potentially an unlimited number
of sources where the structured data are to be found. Each of those sources have
its own logical schema, naming conventions, etc.
Then, the system must know how to communicate with these knowledge bases, and
what strategies to adopt to reduce the computation cost of generating
distributed queries (see section below~\ref{sec:schema-unaware-shortcoming}).
In some cases, it's also critical to aggregate results from different sources.

>>>>

The way translation from NL questions to formal query has evolved over years.
Table~\ref{tab:overview} presents an overview of major systems that we take into
consideration in this survey.

\begin{table}
\centering
\rotatebox{90}{
\begin{minipage}{\textheight}
\begin{tabular}{|c|l|c|c|c|c|c|c|}\hline
%\begin{tabular}{|c|c|c|c|c|c|c|c|}\hline
\multirow{2}{*}{\bf Approach} & \multirow{2}{*}{\bf System}
&
\multicolumn{6}{c|}{\bf Dimensions}\\\cline{3-8}
& & {\bf Query} & {\bf Data} & {\bf Answers} & {\bf Portability} & {\bf
Linguistic coverage} & {\bf Error feedback}\\\hline\hline 
\multirow{2}{*}{Domain-dependent semantic parsing} & {\sc
Baseball}~\cite{Green:1961:BAQ:1460690.1460714} & & & & & & \\\cline{2-8}
& {\sc Lunar}~\cite{Woods:1973:PNL:1499586.1499695} & & & & & & \\\hline
\multirow{5}{*}{Complex question translation} & {\sc
Chat-80}~\cite{Warren:1982:EEA:972942.972944} & & & & + & + & \\\cline{2-8}
& {\sc Irus}~\cite{Bates:1983:IRU:511793.511804} & & & & + & & \\\cline{2-8}
& {\sc Qwerty}~\cite{Nelken:2000:QTD:992730.992808} & & temporal & & - & &
\\\cline{2-8} & {\sc
Precise}~\cite{Popescu:2004:MNL:1220355.1220376,Popescu:2003:TTN:604045.604070}
& & & & & & + \\\cline{2-8}
& {\sc Panto}~\cite{Wang:2007:PPN:1419662.1419706} & & & & & + & + \\\hline
\multirow{5}{*}{Feedback-driven approaches} &
{\sc Masque/SQL}~\cite{Androutsopoulos93masque} & & Prolog/SQL & & + & &
\\\cline{2-8} & {\sc Team}~\cite{Grosz:1987:TED:25672.25674} & & & & + & & + \\\cline{2-8}
& {\sc NaLIX} \& {\sc DaNaLIX}~\cite{Li:2005:NIN:1066157.1066281} & & & & + & &
\\\cline{2-8}
& {\sc C-Phrase}~\cite{Minock:2010:CSB:1715942.1716190} & & & & & &
\\\cline{2-8}
& {\sc
Orakel}~\cite{Cimiano:2007:PNL:1216295.1216330} & & & & + & & \\\hline
\multirow{3}{*}{Learning-based approaches} & Zettlemoyer
et al.~\cite{DBLP:conf/uai/ZettlemoyerC05} & & & & & & \\\cline{2-8}
& Miller et al.~\cite{Miller:1996:FSA:981863.981871} & & & & & & \\\cline{2-8}
& {\sc Wolfie}~\cite{Thompson:2003:AWM:1622420.1622421} & & & & & &
\\\hline
\multirow{2}{*}{Schema-unaware approaches} & {\sc
PowerAqua}~\cite{DBLP:conf/esws/LopezMU06} & & & & & & \\\cline{2-8}
 & {\sc DeepQA}~\cite{DBLP:journals/aim/FerrucciBCFGKLMNPSW10} & & & & & &
 \\\hline
\end{tabular}
\end{minipage}
}
\caption{Overview of major NL interfaces to structured data}
\label{tab:overview}
\end{table}

@@

\subsection{Schema-unaware approaches}
A range of recent systems aggregate potential answers from different sources.
This range of systems have emerged in parallel with the success of the semantic
web technologies. 
The particularity of these approaches, is that they cannot rely on the schema of
underlying knowledge bases, because the different sources are potentially
modelled in very different ways. 
Thus, the set of systems represented by these approaches try to bridge the gap
between user terminologies and the different terminologies used in the different
knowledge bases that the interface talks to.
These approaches can be seen as an extension of several approaches presented
before, namely ``complex question translation'' (because the question is
further analyzed to map it with the terminology used in the different knowledge
bases) and ``learning-based approaches'' (because some of the systems
represented in these approaches contain learning components).

\subsubsection{Terminology mapping}
In previous approaches, end-users were not aware of how data are modeled in the
knowledge base. This requires advanced natural language processing to map user's
terminology with database terminology. In schema-unaware apppraoches, the
systems do not talk to a single database, but to potentially an unlimited number
of sources where the structured data are to be found. Each of those sources has
its own logical schema, naming conventions, etc.
Then, the system must know how to communicate with these knowledge bases, and
what strategies to adopt to reduce the computation cost of generating
distributed queries (see section below~\ref{sec:schema-unaware-shortcoming}).
In some cases, it's also critical to aggregate results from different sources.
